Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2023-03-23 paper-1/elife.tex
Manuscript bugfix

Across networks and stimuli, we found even stronger evidence that the early portion of the network drove adaptation to B. We first confirmed that $\Delta \R{N}{i}$ and $\Delta \T{B}{i}$ were robustly positively correlated (median Pearson's $\rho$ 0.992: T = 7.26e+03, p = 9.86e-22; one-sided Wilcoxon, n = 120). In each network, we then identified the early and late portions with respect to stimulation in B and quantified the median non-target response contrast ($\Delta \R{N}{}$, \FIG{early-adaptation}C) and the median contrast in $\T{B}{}$ ($\Delta \T{B}{}$, \FIG{early-adaptation}D) within these two portions. We found that the response in the early portion was consistently greater in \dev{} than \msc{} ($\Delta \R{B}{early} > 0$: T = 6.98e+03, p = 8.48e-19), unlike the late portion, which decreased ($\Delta \R{B}{late} < 0$: T = 295, p = 1.23e-18; see also \FIG{thresholds-follow-std}D). $\Delta \T{B}{}$ followed the same pattern, with the early portion exhibiting stronger TA in \dev{} (T = 4.63e+03, p = 2.21e-17), while the late portion was instead more recovered (T = 26, p = 2.97e-17).

>>>>

Across networks and stimuli, we found even stronger evidence that the early portion of the network drove adaptation to B. We first confirmed that $\Delta \R{N}{i}$ and $\Delta \T{B}{i}$ were robustly positively correlated (median Pearson's $\rho$ 0.992: T = 7.26e+03, p = 9.86e-22; one-sided Wilcoxon, n = 120). In each network, we then identified the early and late portions with respect to stimulation in B and quantified the median non-target response contrast ($\Delta \R{N}{}$, \FIG{early-adaptation}C) and the median contrast in $\T{B}{}$ ($\Delta \T{B}{}$, \FIG{early-adaptation}D) within these two portions. We found that the response in the early portion was consistently greater in \dev{} than \msc{} ($\Delta \R{N}{early} > 0$: T = 6.98e+03, p = 8.48e-19), unlike the late portion, which decreased ($\Delta \R{N}{late} < 0$: T = 295, p = 1.23e-18; see also \FIG{thresholds-follow-std}D). $\Delta \T{B}{}$ followed the same pattern, with the early portion exhibiting stronger TA in \dev{} (T = 4.63e+03, p = 2.21e-17), while the late portion was instead more recovered (T = 26, p = 2.97e-17).

### 2023-03-23 paper-1/manuscript.tex
Manuscript bugfix

Across networks and stimuli, we found even stronger evidence that the early portion of the network drove adaptation to B. We first confirmed that $\Delta \R{N}{i}$ and $\Delta \T{B}{i}$ were robustly positively correlated (median Pearson's $\rho$ 0.992: T = 7.26e+03, p = 9.86e-22; one-sided Wilcoxon, n = 120). In each network, we then identified the early and late portions with respect to stimulation in B and quantified the median non-target response contrast ($\Delta \R{N}{}$, \FIG{early-adaptation}c) and the median contrast in $\T{B}{}$ ($\Delta \T{B}{}$, \FIG{early-adaptation}d) within these two portions. We found that the response in the early portion was consistently greater in \dev{} than \msc{} ($\Delta \R{B}{early} > 0$: T = 6.98e+03, p = 8.48e-19), unlike the late portion, which decreased ($\Delta \R{B}{late} < 0$: T = 295, p = 1.23e-18; see also \FIG{thresholds-follow-std}d). $\Delta \T{B}{}$ followed the same pattern, with the early portion exhibiting stronger TA in \dev{} (T = 4.63e+03, p = 2.21e-17), while the late portion was instead more recovered (T = 26, p = 2.97e-17).

>>>>

Across networks and stimuli, we found even stronger evidence that the early portion of the network drove adaptation to B. We first confirmed that $\Delta \R{N}{i}$ and $\Delta \T{B}{i}$ were robustly positively correlated (median Pearson's $\rho$ 0.992: T = 7.26e+03, p = 9.86e-22; one-sided Wilcoxon, n = 120). In each network, we then identified the early and late portions with respect to stimulation in B and quantified the median non-target response contrast ($\Delta \R{N}{}$, \FIG{early-adaptation}c) and the median contrast in $\T{B}{}$ ($\Delta \T{B}{}$, \FIG{early-adaptation}d) within these two portions. We found that the response in the early portion was consistently greater in \dev{} than \msc{} ($\Delta \R{N}{early} > 0$: T = 6.98e+03, p = 8.48e-19), unlike the late portion, which decreased ($\Delta \R{N}{late} < 0$: T = 295, p = 1.23e-18; see also \FIG{thresholds-follow-std}d). $\Delta \T{B}{}$ followed the same pattern, with the early portion exhibiting stronger TA in \dev{} (T = 4.63e+03, p = 2.21e-17), while the late portion was instead more recovered (T = 26, p = 2.97e-17).
